Topological approach to finding blackholes in directed networks

### 2019-12-02 blackholes/pavt/article.tex
Results and experimental part

\FIXME{не понял логику абзаца: большая SCC может жрать много времени, граф может из нее состоять, и лучше сжать ее до 1 вершины}

\FIXME{Хорошо бы ссылку на graph condensation}

@@

In this article we use the following algorithm for finding graph condensation.
It was independently proposed by Kosaraju and Sharir back in 1979.\par 
First, we find topological sort of the initial graph. It takes O(E + V).
\begin{definition}
TODO: Topological sort
\end{definition}

@@

Let's consider a closure of a single blackhole root. Let this closure to be acquired by depth-first search, which, basically means, that
we can lay those nodes in topologically sorted order. Also, while traversing this graph, we can calculate size of closure for each node
in the given roots closure. Finally, if some node lays on the i'th position on the topological sort and its closure size is i, than we can
be conclude, that every node with index less than i in the topological sort will be reachable from v(i).

@@

%
\section{Experimental part}
%

>>>>

@@

In this article we use the following algorithm for finding graph condensation.
It was independently proposed by Kosaraju and Sharir back in 1979. \FIXME{Ссылку на эту статью} \par

First, we find topological sort of the initial graph. It takes O(E + V).
\begin{definition}
TODO: Topological sort
\end{definition}

@@

Let's consider a closure of a single blackhole root. Let this closure to be acquired by depth-first search, which, basically means, that
we can lay those nodes in topologically sorted order. Also, while traversing this graph, we can calculate size of closure for each node
in the given roots closure. Finally, if some node lays on the i'th position on the topological sort and its closure size is i, then we can 
conclude, that every node with index less than i in the topological sort will be reachable from v(i).

@@

%
\section{Experimental part}
To demonstrate efficiency of our approach, we conducted a series of experiments. We ran both algorithms (New Jersey team and ours) on a 
set of graphs. \par
For these experiments we chose RMAT, Uniform Random (UR) and SSCA2 graph types. Those were generated for scales from 4 to 22
with step 2. Size i means that graph has 2 pow i nodes and 32 * V edges. Actual count of edges to process can differ from these ideal values, as duplicate edges 
and self-loops are omitted when reading graph from file. \par

\begin{table}[]
\caption{Configurations of experimental graphs}
\label{tabular:tableconfigurations}
\begin{center}
\begin{tabular}{ccc}
Graph Type & Nodes Count & Edges Count \\
RMAT.04 & 16 & 177 \\
RMAT.06 & 64 & 1270 \\
RMAT.08 & 256 & 6663 \\
RMAT.10 & 1024 & 30186 \\
RMAT.12 & 4096 & 126988 \\
RMAT.14 & 16384 & 517554 \\
RMAT.16 & 65536 & 2087072 \\
RMAT.18 & 262144 & 7892410 \\
RMAT.20 & 1048576 & 32993233 \\
RMAT.22 & 4194304 & 67099679 \\
SSCA2.04 & 16 & 120 \\
SSCA2.06 & 64 & 722 \\
SSCA2.08 & 256 & 2668 \\
SSCA2.10 & 1024 & 10529 \\
SSCA2.12 & 4096 & 43603 \\
SSCA2.14 & 16384 & 173477 \\
SSCA2.16 & 65536 & 677649 \\
SSCA2.18 & 262144 & 2724762 \\
SSCA2.20 & 1048576 & 10902287 \\
SSCA2.22 & 4194304 & 43580024 \\
UR.04 & 16 & 207 \\
UR.06 & 64 & 1614 \\
UR.08 & 256 & 7652 \\
UR.10 & 1024 & 32201 \\
UR.12 & 4096 & 130486 \\
UR.14 & 16384 & 523740 \\
UR.16 & 65536 & 2096570 \\
UR.18 & 262144 & 8388074 \\
UR.20 & 1048576 & 33553908 \\
UR.22 & 4194304 & 134217174
\end{tabular}
\end{center}
\end{table}

We've been conducting our experiments on a Linux machine with the following specifications:
\begin{itemize}
    \item OS: Ubuntu 16.04 xenial
    \item Kernel: x86\_64 Linux 4.15.0-46-generic
    \item Shell: bash 4.3.48
    \item CPU: Intel Core i7-8550U CPU @ 4GHz
    \item RAM: 15802MiB
\end{itemize}

All runs were performed in a single-thread mode. We allowed up to 20 minutes of working time for every run. In order to save time,
algorithms did not print out found blackholes, but printed counter on every found and not filtered (by any reason) blackhole.

\begin{table}[H]
\caption{Experimental results}
\label{tabular:tableresults}
\begin{center}
\begin{tabular}{ccccccccc}
Graph & Type & Algorithm & Blackholes & Time & Algorithm & Blackholes & Time \\
RMAT & 04 & NewJersey & 1 & 0.000265422 & TopSort & 1 & 0.000115912 \\
RMAT & 06 & NewJersey & 1 & 0.0121347 & TopSort & 1 & 0.00034812 \\
RMAT & 08 & NewJersey & 1 & 1.66685 & TopSort & 1 & 0.00146486 \\
RMAT & 10 & NewJersey & 6 & 1200 & TopSort & 10 & 0.00684045 \\
RMAT & 12 & NewJersey & 29 & 1200 & TopSort & 971738 & 1200 \\
RMAT & 14 & NewJersey & 187 & 1200 & TopSort & 735128 & 1200 \\
RMAT & 16 & NewJersey & 1192 & 1200 & TopSort & 373705 & 1200 \\
RMAT & 18 & NewJersey & 5176 & 1200 & TopSort & 10286 & 1200 \\
RMAT & 20 & NewJersey & 617 & 1200 & TopSort & 48867 & 1200 \\
RMAT & 22 & NewJersey & 98 & 1200 & TopSort & 0 & 1200 \\
SSCA2 & 04 & NewJersey & 16 & 0.154763 & TopSort & 16 & 0.000189925 \\
SSCA2 & 06 & NewJersey & 11 & 1200 & TopSort & 70 & 0.00121528 \\
SSCA2 & 08 & NewJersey & 42 & 1200 & TopSort & 263314 & 1200 \\
SSCA2 & 10 & NewJersey & 85 & 1200 & TopSort & 114411 & 1200 \\
SSCA2 & 12 & NewJersey & 343 & 1200 & TopSort & 5870 & 1200 \\
SSCA2 & 14 & NewJersey & 1433 & 1200 & TopSort & 323671 & 1200 \\
SSCA2 & 16 & NewJersey & 5829 & 1200 & TopSort & 893376 & 1200 \\
SSCA2 & 18 & NewJersey & 23179 & 1200 & TopSort & 224567 & 1200 \\
SSCA2 & 20 & NewJersey & 92347 & 1200 & TopSort & 24199 & 1200 \\
SSCA2 & 22 & NewJersey & 370770 & 1200 & TopSort & 0 & 1200 \\
UR & 04 & NewJersey & 1 & 0.000223768 & TopSort & 1 & 0.000115029 \\
UR & 06 & NewJersey & 1 & 0.0170713 & TopSort & 1 & 0.000331235 \\
UR & 08 & NewJersey & 1 & 2.30256 & TopSort & 1 & 0.00147483 \\
UR & 10 & NewJersey & 1 & 240.822 & TopSort & 1 & 0.00670724 \\
UR & 12 & NewJersey & 0 & 1200 & TopSort & 1 & 0.034011 \\
UR & 14 & NewJersey & 0 & 1200 & TopSort & 1 & 0.47257 \\
UR & 16 & NewJersey & 0 & 1200 & TopSort & 1 & 3.05003 \\
UR & 18 & NewJersey & 0 & 1200 & TopSort & 1 & 14.5788 \\
UR & 20 & NewJersey & 0 & 1200 & TopSort & 1 & 67.7176 \\
UR & 22 & NewJersey & 0 & 1200 & TopSort & 1 & 373.244
\end{tabular}
\end{center}
\end{table}
